---
title: "MA [46]15: Lab activity 1"
author: "Your Name"
format: gfm
---

# Introduction

In this lab activity we do a preliminary analysis of the socio-economic indices that affect quality of life in large cities. We downloaded the indices by city in 2025 and put them at the `data` folder. We can now load them, along with the `tidyverse` package:

```{r init}
#| message: false
library(tidyverse)
ql <- read_tsv("data/qualitylife.tsv", comment = "#")
```

NOTE: activity instructions come between **`[==[`** and **`]==]`**, you can safely remove these lines in your final version.

# Visualization

Our first visualization is cost of living against pollution:

```{r cl-pi}
#| warning: false
ggplot(ql, aes(`Cost of Living Index`, `Pollution Index`)) + geom_point() + geom_smooth()
```

**`[==[`** Add a smoother to the `cl-pi` chunk above. **`]==]`**

We now investigate how the indices affect quality of life:

**`[==[`** In the chunk below, keep the smoother and color the points by `Quality of Life Index`. **`]==]`**

```{r cl-pi-ql}
#| warning: false
ggplot(ql, aes(`Cost of Living Index`, `Pollution Index`, color = `Quality of Life Index`)) + geom_point() + geom_smooth()
```


## Discussion

**`[==[`** Comment on the relationship between cost of living and pollution and how they seem to affect quality of life. **`]==]`**

Pollution and cost of living are inversely related. A high pollution index is correlated with a low cost of living. High pollution leads to a low quality of life while high cost of living is correlated with a high quality of life.
